\documentclass[10pt]{article}

% Import the templates and custom commands from the external file
\input{resume_templates}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage[letterpaper, margin=0.30in]{geometry}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref} % Hyperlinks setup 
\usepackage{enumitem} % For customizing itemize environments
\usepackage{calc} % For length calculation 
\usepackage{ifthen} % For conditional statements
\usepackage{fontawesome5} % For FontAwesome icons

% Set the spacing values
\setlength{\parskiplength}{0.15em} 
\setlength{\sectionskiplength}{0.25em}

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\customheader{Steve Wang}{(650) 799-2578}{stevewang.at.work@gmail.com}{stevewang2000}{stevewanglog.com}{steve-z-wang}
 
% Skills 
\begin{customsectionnoskip}{Skills}

    \skillgroup{Expertise}{Full-stack Development, Cloud Computing, Data Engineering, Machine Learning} \\ 
    \skillgroup{Languages \& Tools}{Python, Java, JavaScript, C, C++, C\#, SQL, Bash, PostgreSQL, Redis, Docker, Git, Figma} \\ 
    \skillgroup{Frameworks \& Libraries}{AWS, React, Django, Flask, Spring Boot, NumPy, Pandas, Scikit-learn, TensorFlow, PyTorch} 

\end{customsectionnoskip}

% Experience 
\begin{customsection}{Experience}

    \experience{Software Development Engineer}
    {Amazon, Buy with Prime}
    {Seattle, WA}
    {Feb. 2025 -- present}
    {
        \item Refactored code across multiple packages for a GraphQL API service using Python and AWS Lambda.
        \item Reduced codebase size by two-thirds, improving maintainability and reducing technical debt; projected to save 4-6 weeks of team development time for each new API version.
    }

    \experience{Software Development Engineer}
    {AWS, Elastic VMware Service}
    {Seattle, WA}
    {Feb. 2025 -- Apr. 2025}
    {
        \item Led a time-sensitive integration project with the Account Termination Service (Java, AWS), delivering to GA 2 days ahead of schedule.
        \item Wrote and reviewed over 8,000 lines of production code, with a net increase of +5,500 LOC, including core deletion logic, data isolation flows, alarms, dashboards, and pipeline safety checks.
        \item Aligned design with principal engineer, implemented operational tooling, and unblocked production readiness through test automation and documentation.
        \item Ensured team continuity by writing a comprehensive onboarding guide and driving cross-team alignment post-handover.
    }

    \experience{Volunteer}
    {arXiv.org} 
    {Ithaca, NY} 
    {Sept. 2024 -- Dec. 2024}
    {
        \item Developed a field classification system for research papers using large language models (LLM), reducing user error rate and moderator overhead.
        \item Built a web application for research paper submission and review automation (Python, Flask).
    }

    \experience{Software Development Engineer Internship}
    {AWS, Outposts} 
    {Seattle, WA} 
    {Jun. 2024 -- Aug. 2024}
    {
        \item Designed and implemented a business data forecasting service for AWS Snow customers using Python, AWS Lambda, and Redshift, improving planning accuracy.
        \item Developed a machine learning model to predict lead times across various percentiles, utilizing survival analysis and lag features.
        \item Built and deployed pipelines for weekly model retraining and daily batch predictions, ensuring the model stayed accurate with both long-term and short-term data.
        \item Collaborated with internal stakeholders and a UX designer to create a Slack bot interface that improved user accessibility and aligned with customer needs.
    }

    \experience{Research Assistant}
    {Emory Graph Mining Group} 
    {Atlanta, GA} 
    {Sept. 2022 -- Jan. 2023}
    {
        \item Created medical and pharmaceutical training datasets for graph machine learning models (Python, Pandas).
    }
    
\end{customsection}

% Projects 
\begin{customsection}{Projects}

    \project{SQL Query Engine from Scratch (CS 4321: Practicum in Database Systems)}
    {Ithaca, NY}
    {Sept. 2024 -- present} 
    {} 
    { 
        \item Independently built a static SQL query engine (originally designed for a team of four), delivering over 7,500 lines of Java code.
        \item Implemented advanced data processing algorithms—including dynamic heuristic optimization for query plans, external sorting, block nested loop joins, sort-merge joins, B+ tree indexing, page buffer accessing, and a custom serialization format—to enable quick and efficient data access.
    }

    \project{TracCrop: Master’s Degree Capstone Project}
    {Ithaca, NY}
    {Oct. 2023 -- May 2024}
    {JavaScript, Python, React, Django, SQL, Redis, Azure}
    {
        \item Maintained and enhanced an agriculture business and data management platform for North American farmers, streamlining chemical usage, policy compliance, and workforce and task management within a unified system.
        \item Implemented specialized workflow controls and data visualization features based on customer feedback. Developed the front-end interface and corresponding RESTful web services, enhancing agricultural management efficiency.
        \item Developed an automated ETL pipeline to regularly update reference data from public chemical and agricultural sources, ensuring database accuracy and maintaining up-to-date information.
    }

    \project{Multiplayer Rogue-like Game (Software Engineering Course Project)}
    {Atlanta, GA}
    {Sept. 2022 -- Dec. 2022}
    {}
    {
        \item Collaborated with a team of five using Scrum to develop an online, multiplayer, rogue-like pixel game where players control a ghost that can possess enemies.
        \item Created procedurally generated dungeons with prefab-based rooms and corridors for unique level designs.
        \item Developed custom enemy behaviors, interactive logic, and animations, enhancing game difficulty and player engagement.
    }

\end{customsection}

% Education 
\begin{customsection}{EDUCATION}

    \education{Cornell University}{Ithaca, NY}{Sept. 2023 -- Dec. 2024}
    {Master of Engineering in Electrical \& Computer Engineering, GPA: 3.6/4.0}

    \education{Emory University}{Atlanta, GA}{Sept. 2021 -- May 2023}
    {Bachelor of Science in Mathematics \& Computer Science, GPA: 3.6/4.0}

\end{customsection}


% Award
\begin{customsectionnoskip}{Awards \& Achievements}

    \award{Bronze Medal, Top 8\% (69/937)}{Lyft Autonomous Vehicles Motion Prediction, Kaggle Competition}{Nov. 2020}

\end{customsectionnoskip}

% End document
\end{document}
